---
title: "Charts Showcase"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r echo=FALSE, include=FALSE}

library(fairlytics)
library(plotly)
```

In this vignette well review and showcase some examples of the charts and visualization supported by `fairlytics`. The vignette helps with familiarizing the names of the chart functions for the user.

## Deviation Chart

```{r}

library(plotly)

test_df <- data.frame(
   instrument = c("Instrument A", "Instrument B", "Instrument C"),
   active_weight = c(0.002, -0.001, 0.0003)
)

chart <- ActiveWeightsDeviationChart(df = test_df,
                            instrument_col = "instrument",
                            active_weight_col = "active_weight",
                            min_band = -0.0005, 
                            max_band = 0.0005)

ggplotly(chart)

```

## Asset Allocation HeatMap

```{r}

test_df <- data.frame(
  fund = rep(c("Fund A", "Fund B", "Fund C"), each = 3),
  asset_class = rep(c("Equity", "Fixed Income", "Cash"), 3),
  allocation = runif(9, 0, 1)
  )

AssetClassAllocationTable(df = test_df,
                          x_col = "fund",
                          y_col = "asset_class",
                          value_col = "allocation",
                          chart_title = "Asset Allocation Heatmap")

```

## Portfolio Model Table

```{r}

library(plotly)

portfolio_model_df <- data.frame(
  account_code = c('abc', 'xyz', 'test0001'),
  asset_class = c('Equities', 'Bonds', 'Commodities'),
  mkt_value = c(300, 200, 100),
  port_wgt = c(0.5, 0.3, 0.2),
  model_wgt = c(0.4, 0.4, 0.2),
  active_wgt = c(0.1, -0.1, 0.0)
  )

PortfolioModelTable(
  df = portfolio_model_df,
  mkt_value = "mkt_value",
  port_wgt = "port_wgt",
  model_wgt = "model_wgt",
  active_wgt = "active_wgt"
  )


```

## Relative Weight Bar

```{r}

library(plotly)

relative_df <- data.frame(
  instrument = c("Instrument A", "Instrument B", "Instrument C"),
  weight = c(0.1, -0.05, 0.2),
  fund_label = c("Fund 1", "Fund 1", "Fund 2")
  )

chart <- RelativeWeightBarChart(df = relative_df, 
                       instrument_col = "instrument", 
                       weight_col = "weight", 
                       fund_label_col = "fund_label", 
                       txt_abv_grph = 0.02)

ggplotly(chart)

```

## Line Charts

For line charts `fairlytics` support two different plotting engines. You can use highcharter or ggplot2 as your plotting engine.

### ggplot Line Chart

```{r }

library(ggplot2)
library(plotly)
library(lubridate)

test_data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = runif(10),
  ColorGroup = rep(c("Red", "Blue"), each = 5),
  Group = rep(c("A", "B"), each = 5)
  )

chart <- LineChart(
  df = test_data,
  x_col = "Date",
  y_col = "Value",
  color_col = "ColorGroup",
  group_col = "Group",
  chart_title = "ggplot Line Chart",
  percent_y_axis = TRUE
  )

ggplotly(chart)

```

### Highcharter Line Chart

```{r }

library(highcharter)
library(lubridate)

data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = rnorm(10),
  Group = rep(c("A", "B"), each = 5)
  )

LineChartr(
  df = data,
  x_col = "Date",
  y_col = "Value",
  color_col = NULL,
  group_col = "Group",
  chart_title = "Highcharter Line Chart"
  )

```

## line chart wrapper

`LineChartWrapper` function can be used to create a line chart and you can specify which plot engine to use between ggplot2 and highcharter.

```{r }

library(ggplot2)
library(plotly)
library(highcharter)
library(lubridate)

data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = runif(10),
  ColorGroup = rep(c("Red", "Blue"), each = 5),
  Group = rep(c("A", "B"), each = 5)
  )

```

### using ggplot2

```{r}


chart_ggplot2 <- LineChartWrapper(
  df = data,
  x_col = "Date",
  y_col = "Value",
  color_col = "ColorGroup",
  group_col = "Group",
  chart_title = "Interactive Line Chart (ggplot2)",
  plot_engine = "ggplot2"
)

ggplotly(chart_ggplot2)

```

### using HighCharter

```{r}

LineChartWrapper(
  df = data,
  x_col = "Date",
  y_col = "Value",
  color_col = "ColorGroup",
  group_col = "Group",
  chart_title = "Line Chart Highcharter)",
  plot_engine = "highcharter"
  )

```

## Bar Charts

For bar charts `fairlytics` support two different plotting engines. You can use highcharter or ggplot2 as your plotting engine.

Types of bar charts supported are 'group' and 'stack', this can be set via the `bar_type` parameter.

To Sort the bars on chart you have to set the parameter `ordering_bars = TRUE` and then pick whether to sort in an ascending order by setting `ascending = TRUE`or `ascending = TRUE` for descending order.

You can Flip the chart axis by setting `chart_flip = TRUE`.

### Using the Bar Chart Wrapper

```{r }

library(ggplot2)
library(highcharter)
library(lubridate)

test_df <- data.frame(
    category = c("A", "B", "C"),
    value = c(10, 20, 15),
    group = c("X", "Y", "X")
  )

chart <- BarChart(test_df, 
                  x_col = "category",
                  y_col = "value",
                  color_col = "group",
                  bar_type = "stack",
                  plot_engine = "ggplot2")

ggplotly(chart)

```

#### Bar Type = 'group'
```{r }

library(highcharter)
library(lubridate)

library(tibble)

test_data <- data.frame(
  "Name" = rep(c("EQT 1", "EQT 2", "EQT 3", "EQT 4"), length.out = 9),
  "Fund" = rep(c("Fund A", "Fund B", "Fund C"), length.out = 9),
  "value" = runif(9, 0, 1)
)

chart <- BarChart(test_data, 
                  x_col = "Fund",
                  y_col = "value",
                  color_col = "Name",
                  bar_type = "group",
                  plot_engine = "ggplot2")

ggplotly(chart)

```


#### Bar Type = 'stack'
```{r }

library(highcharter)
library(lubridate)

library(tibble)

test_data <- data.frame(
  "Name" = rep(c("EQT 1", "EQT 2", "EQT 3", "EQT 4"), length.out = 9),
  "Fund" = rep(c("Fund A", "Fund B", "Fund C"), length.out = 9),
  "value" = runif(9, 0, 1)
)

chart <- BarChart(test_data, 
                  x_col = "Fund",
                  y_col = "value",
                  color_col = "Name",
                  bar_type = "stack",
                  plot_engine = "ggplot2")

ggplotly(chart)

```


### ggplot Bar Chart

```{r }

library(ggplot2)
library(plotly)

test_df <- data.frame(
  category = c("A", "B", "C"),
  values = c(0.3, 0.5, 0.2),
  color = c("red", "green", "blue")
)
chart <- BarChart_ggplot(test_df, 
                         x_col = "category",
                         y_col = "values",
                         color_col = "color",
                          bar_type = "stack",
                         chart_title = "Ordered Bar Chart", 
                         show_bar_text = TRUE)

ggplotly(chart)

```

### Highcharter Bar Chart

```{r }

library(highcharter)
library(lubridate)

data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = rnorm(10),
  Group = rep(c("A", "B"), each = 5)
  )

BarCharter(test_df,
           x_col = "category",
           y_col = "values",
           color_col = "color",
           bar_type = "stack",
           chart_title = "Ordered Bar Chart",
           show_bar_text = TRUE)

```

## Area Chart

```{r}

library(ggplot2)
library(plotly)

test_data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = runif(10),
  FillGroup = rep(c("Red", "Blue"), each = 5),
  Group = rep(c("A", "B"), each = 5)
)

chart <- AreaChart(
  df = test_data,
  x_col = "Date",
  y_col = "Value",
  fill_col = "FillGroup",
  group_col = "Group",
  chart_title = "Interactive Area Chart"
)

ggplotly(chart)

```

## Pie Chart

```{r}

library(ggplot2)

test_data <- data.frame(
  category = c("A", "B", "C"),
  values = c(0.3, 0.5, 0.2)
)

PieChart(test_data,
         value_col = "values",
         color_col = "category",
         chart_title = "Example Pie Chart")

```

## Donut Chart

```{r}

library(plotly)

test_df <- data.frame(
  category = c("A", "B", "C"),
  values = c(30, 50, 20)
)

DonutPlotly(test_df,
            value_col = "values",
            label_col = "category",
            chart_title = "Example Donut Chart")


```

## Calender Returns Table

```{r }

returns_df <- data.frame(
  Year = c(2023, 2024),
  Jan = c(0.05, 0.04),
  Feb = c(0.02, 0.03),
  Mar = c(0.02, 0.03),
  Apr = c(-0.01, 0.00),
  May = c(-0.2, 0.00),
  Jun = c(-0.01, 0.00),
  Jul = c(-0.01, 0.00),
  Aug = c(-0.01, 0.01),
  Sep = c(-0.01, 0.00),
  Oct = c(-0.01, 0.00),
  Nov = c(-0.01, 0.00),
  Dec = c(-0.01, 0.00),
  YTD = c(0.06, 0.07)
  )

CalendarReturnsTable(returns_df)

```
