---
title: "Charts Showcase"
format: html
editor: visual
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r echo=FALSE, include=FALSE}

library(fairlytics)

```


In this vignette well review and showcase some examples of the charts and visualization supported by `fairlytics`. 
The vignette helps with familiarizing the names of the chart functions for the user.


## Deviation Chart

```{r}


test_df <- data.frame(
   instrument = c("Instrument A", "Instrument B", "Instrument C"),
   active_weight = c(0.002, -0.001, 0.0003)
)

ActiveWeightsDeviationChart(df = test_df,
                            instrument_col = "instrument",
                            active_weight_col = "active_weight",
                            min_band = -0.0005, 
                            max_band = 0.0005)


```


## Asset Allocation HeatMap

```{r}

test_df <- data.frame(
  fund = rep(c("Fund A", "Fund B", "Fund C"), each = 3),
  asset_class = rep(c("Equity", "Fixed Income", "Cash"), 3),
  allocation = runif(9, 0, 1)
  )

AssetClassAllocationTable(df = test_df,
                          x_col = "fund",
                          y_col = "asset_class",
                          value_col = "allocation",
                          chart_title = "Asset Allocation Heatmap")

```


## Portfolio Model Table

```{r}

portfolio_model_df <- data.frame(
  account_code = c('abc', 'xyz', 'test0001'),
  asset_class = c('Equities', 'Bonds', 'Commodities'),
  mkt_value = c(300, 200, 100),
  port_wgt = c(0.5, 0.3, 0.2),
  model_wgt = c(0.4, 0.4, 0.2),
  active_wgt = c(0.1, -0.1, 0.0)
  )

PortfolioModelTable(
  df = portfolio_model_df,
  mkt_value = "mkt_value",
  port_wgt = "port_wgt",
  model_wgt = "model_wgt",
  active_wgt = "active_wgt"
  )


```


## Relative Weight Bar

```{r}

relative_df <- data.frame(
  instrument = c("Instrument A", "Instrument B", "Instrument C"),
  weight = c(0.1, -0.05, 0.2),
  fund_label = c("Fund 1", "Fund 1", "Fund 2")
  )

RelativeWeightBarChart(df = relative_df, 
                       instrument_col = "instrument", 
                       weight_col = "weight", 
                       fund_label_col = "fund_label", 
                       txt_abv_grph = 0.02)

```


## Line Charts

For line charts `fairlytics` support two different plotting engines. You can use highcharter or ggplot2 as your plotting engine.


### ggplot Line Chart

```{r }

library(ggplot2)
library(plotly)
library(lubridate)

test_data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = runif(10),
  ColorGroup = rep(c("Red", "Blue"), each = 5),
  Group = rep(c("A", "B"), each = 5)
  )

LineChart(
  df = test_data,
  x_col = "Date",
  y_col = "Value",
  color_col = "ColorGroup",
  group_col = "Group",
  chart_title = "ggplot Line Chart"
  )


```


### Highcharter Line Chart

```{r }

library(highcharter)
library(lubridate)

data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = rnorm(10),
  Group = rep(c("A", "B"), each = 5)
  )

LineChartr(
  df = data,
  x_col = "Date",
  y_col = "Value",
  color_col = NULL,
  group_col = "Group",
  chart_title = "Highcharter Line Chart"
  )

```



## line chart wrapper

`LineChartWrapper` function can be used to create a line chart and you can specify which plot engine to use between ggplot2 and highcharter.

```{r }

library(ggplot2)
library(plotly)
library(highcharter)
library(lubridate)

data <- data.frame(
  Date = seq.Date(from = Sys.Date() - 10, by = "day", length.out = 10),
  Value = runif(10),
  ColorGroup = rep(c("Red", "Blue"), each = 5),
  Group = rep(c("A", "B"), each = 5)
  )

```

### using ggplot2

```{r}


chart_ggplot2 <- LineChartWrapper(
  df = data,
  x_col = "Date",
  y_col = "Value",
  color_col = "ColorGroup",
  group_col = "Group",
  chart_title = "Interactive Line Chart (ggplot2)",
  plot_engine = "ggplot2"
)

chart_ggplot2

```


### using HighCharter

```{r}

LineChartWrapper(
  df = data,
  x_col = "Date",
  y_col = "Value",
  color_col = "ColorGroup",
  group_col = "Group",
  chart_title = "Line Chart Highcharter)",
  plot_engine = "highcharter"
  )

```


## Calender Returns Table

```{r }

returns_df <- data.frame(
  Year = c(2023, 2024),
  Jan = c(0.05, 0.04),
  Feb = c(0.02, 0.03),
  Mar = c(0.02, 0.03),
  Apr = c(-0.01, 0.00),
  May = c(-0.2, 0.00),
  Jun = c(-0.01, 0.00),
  Jul = c(-0.01, 0.00),
  Aug = c(-0.01, 0.01),
  Sep = c(-0.01, 0.00),
  Oct = c(-0.01, 0.00),
  Nov = c(-0.01, 0.00),
  Dec = c(-0.01, 0.00),
  YTD = c(0.06, 0.07)
  )

CalendarReturnsTable(returns_df)

```

