---
title: "Introduction to fairlytics"
format: html
editor: visual
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

The `fairlytics` package is a comprehensive toolkit developed to streamline and enhance data workflows. Designed by our team for internal use, it offers a carefully curated collection of essential functions that cater to a wide range of tasks, including:

-   **Data Cleaning:** Simplify and automate the process of preparing raw data for analysis.

-   **Data Manipulation:** Effortlessly reshape and transform datasets to extract meaningful insights.

-   **Data Visualization:** Create intuitive and impactful visualizations that communicate key findings effectively.

-   **Data Analysis:** Leverage robust analytical tools to uncover trends and drive data-driven decisions.

### Why use fairlytics?

The `fairlytics` package is built to:

-   **Enhance Productivity:** Reduce the time spent on repetitive tasks with ready-to-use functions.

-   **Ensure Consistency:** Maintain uniformity in data processing and analysis across projects.

-   **Promote Collaboration:** Provide a shared library of tools that reflect best practices and team standards.

### Installation

To install and begin using the `fairlytics` package, use the following commands:

```{r  eval=FALSE, echo=TRUE}

# Uncomment if devtools is not installed
# install.packages("devtools")
devtools::install_github("menzy17/fairlytics")

# Load the package
library(fairlytics)

```


### Getting Help

For detailed documentation and examples, refer to function documentation:

```{r eval=FALSE, echo=TRUE}

# replace foo with the actual function name
?fairlytics::foo

```



